Workflow

### 2014-08-01 Workflow/Workflow.Rmd
Updates to Workflow file.

### Create historical data frame
* Run `Scripts/PreProcess.R -S <Source>` to create the historical data frame for `<Source>`.
The file will be stored at `Packages/EconData/data/<Source>.rda`.
This command is fast; it can be run on a laptop.    
* Build and reload the `EconData` package.    
* Push the changes to GitHub.   
* On acc, Pull from GitHub.     
* On node-00, say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.
This makes the historical data available to the nodes of dahl.
This command doesn't work from fs1 or any of the other nodes of dahl (node-01 through node-42).

>>>>

### Create historical data frame
* Run `Scripts/PreProcess.R -S <Source>` to create the historical data frame for `<Source>`.
The file will be stored at `Packages/EconData/data/<Source>.rda`.
This command is fast; it can be run on a laptop.    
* Build and reload the `EconData` package on a local machine.    
* Push the changes to GitHub.   
* On acc, Pull from GitHub.     
* Install the `EconData` package from GitHub to dahl
    + `ssh` to node-00 on dahl.   
    + Open an R shell by saying `R` at the command prompt.    
    + Say `require(devtools)`.
    + Say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.

This makes the historical data available to the nodes of dahl.
This command doesn't work from fs1 or any of the other nodes of dahl (node-01 through node-42).
